Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
working on electronics system eignieering. moved a figure or something before. changed name of camera control board to pantilt control board.

We felt the Paparazzi system was full featured and proven, and we wanted to adapt it to our needs.

@@

The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symmetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} wings supported 64 lbs (250\% of the maximum take-off weight) under static loading.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.
\begin{wrapfigure}{r}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_sandbagtest.jpg}
	\caption{Load testing the underside of the \emph{Daedalus}'s wings. Shown with 16lbs of load.}
	\label{fig:sandbagtest}
\end{wrapfigure}
A second test was designed to certify the wing could take a top loading present from a 1.5$g$ acceleration with a safety factor of 1.5, and to certify that load could be transmitted to the ground through the fuselage and landing gear. With the aircraft fully assembled and sitting upright on the landing gear, we loaded the top of the wing along the quarter chord with 64 lbs of sandbags. As in our first test, we also rocked the plane \degrees{10} side to side to simulate uneven loading. Our post-test structure inspection once again found no warped members or cracked joints.

@@

We took advantage of the MHS-PM5's swiveling lens assembly 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation. Figures \ref{fig:pantilt} and \ref{fig:pantilt_linkdetail} show the camera lens tilted at \degrees{45} below the horizon.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembly. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{1260} rotation (3.5 revolutions). Both servos are powered and controlled by the Camera Control board.

>>>>

We felt the Paparazzi system was full featured and proven, but we weren't satisified with the capabilities of the existing Paparazzi hardware. The ``Tiny'' v2.1\cite{paparazzi_tinyv21}, the latest

@@

 \begin{wrapfigure}{r}{0.4\textwidth}
	\includegraphics[width=0.37\textwidth]{../images/daedalus_sandbagtest.jpg}
	\caption{Load testing the underside of the \emph{Daedalus}'s wings. Shown with 16lbs of load.}
	\label{fig:sandbagtest}
\end{wrapfigure}
The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symmetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} wings supported 64 lbs (250\% of the maximum take-off weight) under static loading.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.

A second test was designed to certify the wing could take a top loading present from a 1.5$g$ acceleration with a safety factor of 1.5, and to certify that load could be transmitted to the ground through the fuselage and landing gear. With the aircraft fully assembled and sitting upright on the landing gear, we loaded the top of the wing along the quarter chord with 64 lbs of sandbags. As in our first test, we also rocked the plane \degrees{10} side to side to simulate uneven loading. Our post-test structure inspection once again found no warped members or cracked joints.

@@

We took advantage of the MHS-PM5's swiveling lens assembly 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation. Figures \ref{fig:pantilt} and \ref{fig:pantilt_linkdetail} show the camera lens tilted at \degrees{45} below the horizon.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembly. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{1260} rotation (3.5 revolutions). Both servos are powered and controlled by the Pan-tilt control board.
